** INSERT TITLE **

### 2016-02-24 papers/msystems_2016/Schloss_Commentary_mSystems_2016.Rmd
Edit legend to remove VSEARCH from closed-reference clustering

**Figure 1. Comparison of OTU quality generated by multiple algorithms applied to four datasets.** The nearest, average, and furthest neighbor clustering algorithms were used as implemented in mothur (v.1.37). Abundance (AGC) and Distance-based greedy clustering (DGC) were implemented using USEARCH (v.6.1) and VSEARCH (v.1.5.0). Other *de novo* clustering algorithms included Swarm (v.2.1.1), OTUCLUST (v.0.1), and SUMACLUST (v.1.0.20). The MCC values for Swarm were determined by selecting the distance threshold that generated the maximum MCC value for each dataset. The USEARCH and SortMeRNA (v.2.0) closed-reference clusterings were performed using QIIME (v.1.9.1) and the VSEARCH closed-reference clusterings were performed substituting VSEARCH for USEARCH in the QIIME workflows. The order of the sequences in each dataset was randomized thirty times and the intra-method range in MCC values was smaller than the plotting symbol. MCC values were calculated in mothur.

>>>>

**Figure 1. Comparison of OTU quality generated by multiple algorithms applied to four datasets.** The nearest, average, and furthest neighbor clustering algorithms were used as implemented in mothur (v.1.37). Abundance (AGC) and Distance-based greedy clustering (DGC) were implemented using USEARCH (v.6.1) and VSEARCH (v.1.5.0). Other *de novo* clustering algorithms included Swarm (v.2.1.1), OTUCLUST (v.0.1), and SUMACLUST (v.1.0.20). The MCC values for Swarm were determined by selecting the distance threshold that generated the maximum MCC value for each dataset. The USEARCH and SortMeRNA (v.2.0) closed-reference clusterings were performed using QIIME (v.1.9.1). The order of the sequences in each dataset was randomized thirty times and the intra-method range in MCC values was smaller than the plotting symbol. MCC values were calculated in mothur.
